---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SSHelper

<!-- badges: start -->
<!-- badges: end -->
# SSHelper
  SSHelper assists library catalog searches to identify if a source is present within the library collection at Smith College:
  * `library search` searches for a source in the Smith College library.

## Why the project is useful?
  SSHelper is more straight forward way of identifying if a source is present in the library catalog. 
  Ideally we wanted this package to also scrap PDFs of researcher bibliographies and search the catalog 
  from the work cited page directly.
  
## Installation
```{r, eval = FALSE}
# The easiest way to install the whole SSHelper package:
install.packages("SSHelper")
```

## Where users can get help with your project?
To get a bug fix or to use a feature from the development version, you can email 
the students who created the project: fndanu@smith.edu, samuzu@smith.edu, and sghebreghiorgis@smith.edu.

## Who maintains and contributes to the project?
This package was created for Prof. Will Hopper's SDS 270: Advance Programming course in Fall 2023.
