---
title: "Intro_SSHelper"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{knitr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SSHelper)
```

# SSHelper 

The `SSHelper` package provides a r interface to retrieve catalog information from the Smith College library catalog (https://libtools.smith.edu/bento/results.php?) website and allows users to select specific source and view its cover.

## Browsing Sources

Given a title and source type via a user input the `SSHelper()` 
web scrapes the catalog and converts the URL into  
a JSON object with metadata about that catalog.
This is a basic example which shows you how to solve a common problem:

```{r example}
library(SSHelper)
Lists_title <- library_search("1984","journals") 
Lists_title
```


The most useful: thing you can do with these object is plot them, 
using the draw_image which displays the source cover
image in your plot window

```{r}
plot(lists_title)
```

